Creating optimal conditions for reproducible data analysis in R with \pkg{fertile}

### 2020-01-04 fertile_sdss.Rnw
edited abstract examples

Proactively, the package identifies potential mistakes as they are made by the user and outputs an informative message as well as a recommended solution. For example, \pkg{fertile} catches when a user passes a potentially problematic file path---such as an absolute path, or a path that points to a location outside of the project directory---to a variety of common input/output functions. \pkg{fertile} is even more aggressive with functions (like \cmd{setwd()}) that are almost certain to break reproducibility---it causes them to throw errors.

@@

<<message=FALSE>>=
library(tidyverse)
library(fertile)
is_path_portable(".")
is_path_portable("~")
@

@@

<<>>=
file.exists("~/Desktop/my_data.csv")
read.csv("~/Desktop/my_data.csv")
@

>>>>

Proactively, the package identifies potential mistakes as they are made by the user and outputs an informative message as well as a recommended solution. For example, \pkg{fertile} catches when a user passes a potentially problematic file path---such as an absolute path, or a path that points to a location outside of the project directory---to a variety of common input/output functions.

<<message = FALSE>>=
library(fertile)
file.exists("~/Desktop/my_data.csv")
read.csv("~/Desktop/my_data.csv")
@

\pkg{fertile} is even more aggressive with functions (like \cmd{setwd()}) that are almost certain to break reproducibility---it causes them to throw errors.

<<message=FALSE>>=
setwd("~/Desktop")
@

@@

<<message=FALSE>>=
library(tidyverse)
library(fertile)

is_path_portable(".")
is_path_portable("~")

is_data_file("~/Desktop/my_data.csv")
is_image_file("~/Desktop/my_data.csv")
@

@@
